\textbf{Urban mobility in Latin America after COVID-19}

### 2024-01-20 manuscript/manuscript.tex
update intro

\date{}
\begin{document}
\maketitle
\begin{abstract}
The COVID‐19 pandemic has impacted the national systems of population
movement around the world.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, interior hidden, sharp corners, breakable, borderline west={3pt}{0pt}{shadecolor}, frame hidden, enhanced]}{\end{tcolorbox}}\fi

@@

\hypertarget{the-impact-of-covid-19-on-patterns-of-urban-mobility}{%
\subsection{The impact of COVID-19 on patterns of urban
mobility}\label{the-impact-of-covid-19-on-patterns-of-urban-mobility}}

>>>>

\date{}
\begin{document}
\maketitle
\begin{abstract}
The COVID‐19 pandemic has impacted the national systems of population
movement around the world.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, sharp corners, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable]}{\end{tcolorbox}}\fi

@@

\hypertarget{the-impact-of-covid-19-on-urban-mobility}{%
\subsection{The impact of COVID-19 on urban
mobility}\label{the-impact-of-covid-19-on-urban-mobility}}
